Backward designing a reproducible framework for undergraduate data science research

### 2019-12-04 Rmd/jse-2019-ms.Rmd
udpated intro & README
updates
upd
updated methods

---
title: 'A framework for mentored data science research'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
output: 
  - github_document
  - pdf_document
---

>>>>

---
title: 'Backward designing a reproducible framework for undergraduate data science research'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
output: 
  - bookdown::pdf_document2
  - bookdown::html_document2
---

### 2019-12-04 Rmd/methods.Rmd
updated methods

We used backward design principles to create and implement a 
framework for mentored undergraduate data science research 
projects with big data. Below, we describe our use of 
backward design and ideas from @nolan2010computing.
We then detail our framework and its initial implementation.

@@

We used the backward design principles from @wiggins2005understanding 
to create a framework for undergraduate data science research. 
Following @wiggins2005understanding, we identified desired results, 
determined acceptable evidence, and planned learning experiences.

In establishing framework priorities, we categorized all terms from Figure 1 of @nolan2010computing into 3 categories: 
1. worth being familiar with 
1. important to know and do
1. enduring understanding

>>>>

We used backward design principles to create and implement a 
framework for mentored undergraduate data science research 
projects with big data. Below, we describe our use of 
backward design with ideas from @nolan2010computing.
We then detail our framework and its initial implementation.

@@

We used backward design principles from @wiggins2005understanding 
to create a framework for undergraduate data science research. 
Following @wiggins2005understanding, we identified desired results, 
determined acceptable evidence, and planned learning experiences.

Before we identified desired results, we prioritized topics from 
@nolan2010computing. Specifically, we assigned all terms from Figure 1 
of @nolan2010computing into one of three categories:

1. worth being familiar with 
1. important to know and do
1. enduring understanding

```{r table1, echo = FALSE}
library(magrittr)
circles <- tibble::tibble(Class = 1:3, Circle = c("Worth being familiar with", "Important to know and do", "Enduring understanding"))
readr::read_csv("../data/nolan-figure1-circles.csv") %>%
  dplyr::left_join(circles) %>%
  dplyr::arrange(desc(Class)) %>%
  dplyr::select(- Class) %>%
  gt::gt() %>%
  gt::tab_header(title = "Prioritizing Key Terms from Figure 1 of @nolan2010computing", 
                 subtitle ="xxx" ) %>%
  gt::as_latex()
```
